---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
# Welcome to the dev-version of jointest R package

<!-- #[library flipscores on CRAN](http://cran.r-project.org/web/packages/flipscores/index.html) -->


* * *

## Set up

To **install** this github version type (in R):

    ##if devtools is not installed yet: 
    ## install.packages("devtools") 
    library(devtools)
    install_github("livioivil/jointest")


<!-- ## Some examples -->



## A (minimal) example

```{r,  message = FALSE}
n=20
set.seed(123)
D=data.frame(X=rnorm(n),Z1=rnorm(n),Z2=rnorm(n))
D$Y=D$Z1+D$X+rnorm(n)
mod1=glm(Y~X+Z1+Z2,data=D)
mod2=glm(Y~X+poly(Z1,2)+Z2,data=D)
mod3=glm(Y~X+poly(Z1,2)+poly(Z2,2),data=D)
mod4=glm(Y~X+Z1+poly(Z2,2),data=D)
mods=list(mod1=mod1,mod2=mod2,mod3=mod3,mod4=mod4)
for(i in 1:length(mods))
 mods[[i]]$call$data=eval(D)
library(jointest)
res=join_flipscores(mods,n_flips = 5000, score_type = "effective" ,
       seed = 1, tested_coeffs = "X")
summary(res)
summary(combine(res))
res=p.adjust.fwer(res)
summary(res)

```


## References

J Hemerik, JJ Goeman and L Finos (2019) Robust testing in generalized linear models by sign-flipping score contributions, Submitted, arXiv: 1909.03796

<https://arxiv.org/abs/1909.03796>

## Bug reports
If you encounter a bug, please file a
[reprex](https://github.com/tidyverse/reprex) (minimal reproducible example)
on [github](https://github.com/livioivil/jointest/issues).